### 2018-07-24 doc/plos/text/manuscript.tex
discuss Naive Oracle in manuscript

Although the units of ground truth (i.e. wILI) are the same in all locations,
the normal range of wILI varies between locations. To facilitate comparison
between locations, we also report mean absolute scaled error (MASE)
\cite{hyndman2006another}. MASE is the MAE of a given nowcast normalized by the
MAE of a naive nowcast in the same location. We define the naive nowcast for
any given location on any given week as the reported ground truth in the same
location 52 weeks earlier. Using the same notation as above, and considering
the $m$ weeks for which ground truth is available for at least 52 weeks prior,
MASE is defined as:

\begin{align*}
  \text{MASE} &= \text{MAE} \left( \frac{1}{m} \sum_{w=1}^m{\left|x_w - x_{w - 52}\right|} \right) ^ {-1}
\end{align*}

>>>>

Although the units of ground truth (i.e. wILI) are the same in all locations,
the normal range of wILI varies between locations. To facilitate comparison
between locations, we also report mean absolute scaled error (MASE)
\cite{hyndman2006another}. MASE is the MAE of a given nowcast normalized by the
MAE of a one-step naive nowcast computed in-sample in the same location.

Because wILI is subject to revision over multiple months, a real-time naive
nowcast would be defined as \textit{preliminary} wILI on the preceding week.
However, preliminary versions of wILI are not generally known today (except for
within a narrow set of locations and seasons). As a result, we introduce the
``Naive Oracle'' nowcaster. This assumes (incorrectly) that the final version
of wILI is known with no delay and defines the naive nowcast as \textit{final}
wILI on the preceding week. Since this information is not available at runtime,
the Naive Oracle is unfairly advantaged. As such, MASE is reasonably subject to
being greater than one, indicating that the nowcast under consideration
performed \textit{worse} than the ``naive'' nowcast. This should be
unsurprising, if not expected, given that the Naive Oracle incorporates
information which is not available at runtime. In any case, MASE is a useful
measure for comparing the performance of a given nowcast across different
locations.

Given the above discussion of the Naive Oracle, we define the naive nowcast for
any given location on any given week as the final value of ground truth in the
same location one week earlier. Using the same notation as above, and
considering the $m$ weeks for which ground truth is available on the prior
week, MASE is defined as:

\begin{align*}
  \text{MASE} &= \text{MAE} \left( \frac{1}{m} \sum_{w=1}^m{\left|x_w - x_{w - 1}\right|} \right) ^ {-1}
\end{align*}
